---
title: "World Date"
author: "Bongani Mbigi, Daniel Stroe, Cortney Thomas, Jacob, Kurt Kranz"
output:
  html_notebook:
    code_folding: hide
    toc: true
    toc_depth: 4
    toc_float: true
runtime: shiny
---

```{r setup, include=FALSE}
library(tidyverse)
require(data.world)
library(class)
require(data.world)
require(ggplot2)
require(MASS)

data.world::set_config(cfg_env("DW_API"))
knitr::opts_chunk$set(echo = TRUE)
```
  
## **R Session Info**  

```{r}
sessionInfo()
```

## **Github Link** 

[Github]( https://github.com/bongani-m/f17daproject2-mbigi-stroe-kranz-thomas-rodenbusch)

## **Connecting to data.world** 
```{r}
project <- "https://data.world/cct685/bank-marketing"
df <- data.world::query(
  data.world::qry_sql("SELECT * FROM banking_data"),
  dataset = project)
```

# Bank Marketing Data Set 

The data is related with direct marketing campaigns of a Portuguese banking institution. The marketing campaigns were based on phone calls. Often, more than one contact to the same client was required, in order to access if the product (bank term deposit) would be ('yes') or not ('no') subscribed. 


## **K Nearest Neighbors** 
Here we use K Nearest Neighbors to predict the likely hood of whether they subscribed based on Duration of the call and current balance of an existing account.

Interesting insights that was seen was that  accurracy of the model was 85.12241%, which is very accurrate however when viewing a cross table we see that the model has a tendency to report false neggatives (44.1860%) far more than it does false positives(8.314088%),

```{r}
Xy=cbind(df$balance,df$duration)
bank.knntrain=df$month != "jun"
knn.pred=knn(Xy[bank.knntrain,],Xy[!bank.knntrain,],df$y[bank.knntrain],k=1)
table(knn.pred,df$y[!bank.knntrain])
mean(knn.pred==df$y[!bank.knntrain])
renderPlot({
  ggplot(subset(df, month = "jun"),aes(balance, duration, color=y==knn.pred)) + geom_point()
  })
```


## Linear Discriminant Analysis

Using Linear Discriminant Analysis on the same parameteres (duration and current balance) we were able to bost the accurracy to over 90%. This suggest there is a linear releation between whether or not they decide vs duration and balance.

```{r}
bank.ldasubset <- sample(1:150, 75)
lda.fit=lda(y~balance+duration,data=df, subset= bank.ldasubset)
lda.fit

renderPlot({
  ggplot(lda.fit, aes(x = ))
})
bank.ldatrain=subset(df,df$month=="jun")
bank.ldapredict = predict(lda.fit, df[-bank.ldasubset, ])
data.frame(bank.ldapredict)[1:5,]
dflda = data.frame(bank.ldapredict)
lda.class = predict(lda.fit, bank.ldatrain)
table(lda.class$class,bank.ldatrain$y)
mean(lda.class$class==bank.ldatrain$y)
```

## Linear Discriminant Analysis

Using Linear Discriminant Analysis on the same parameteres (duration and current balance) we were able to bost the accurracy to over 90%. This suggest there is a linear releation between whether or not they decide vs duration and balance.

```{r}
bank.glmsubset <- sample(1:150, 75)
df$y_int <- as.integer(as.logical(df$y))
glm.fit=glm(y_int~balance+duration,data=df, subset = bank.glmsubset, family=binomial)
glm.fit
summary(glm.fit)
glm.probs=predict(glm.fit, newdata = df[-bank.glmsubset,], type="response")

glm.pred=ifelse(glm.probs >0.5, 1, 0)

table(glm.pred,df$y_int[-bank.glmsubset])
mean(glm.pred == df$y_int[-bank.glmsubset])
```


## quadratic discriminant analysis

```{r}
bank.qdasubset=df$month != "jun"
qda.fit = qda(y~balance+duration, data = df, subset=bank.qdasubset)
qda.fit # Notice - no coeficients.
bank.qdatrain = subset(df, month == "jun")
bank.qdapredict = predict(qda.fit, df[-bank.qdasubset, ])
data.frame(bank.qdapredict)[1:5,]
dfqda = data.frame(bank.qdapredict)
data.frame(bank.qdatrain)[1:5,]
qda.class = predict(qda.fit, bank.qdatrain)
table(qda.class$class,bank.qdatrain$y)
mean(qda.class$class==bank.qdatrain$y)
```